Inverse energy transfer in three-dimensional quantum vortex flows

### 2025-04-25 revision/referee-response.tex

\documentclass[a4paper,10pt]{letter}
\usepackage[margin=1in]{geometry}
\usepackage{lipsum}
\usepackage{xcolor}
\def\red#1{\textcolor{red}{#1}}

\begin{document}

\begin{enumerate}
    \item The total helicity during the reconnection event is not conserved. The presence of the mutual friction force introduces a dissipation into the normal fluid. Overall, by computing the helicity in the superfluid component, we confirmed this. We decided to omit this plot from the manuscript so as to not introduce further concepts of superfluid helicity to a paper whose narrative is normal fluid centric. We have addressed the referees concern by inserting an additional statement to clarify that the helicity during the reconnection event is not in fact conserved. 
    \item In the timescale of the simulation, we only observe one pair of the vortices which reconnect.  
    \item 
    \item 
    \item The value $t_0$ should in fact be $t_R$, the typo has been corrected.
    \item The authors agree with the comment of the referee that the current notation is not ideal. Instead, the figures have been changed to use the timescale in the horizontal axis of all time plots. Additionally to note, we have replaced the vertical axis label of Fig. 3b with $E_R/\tau_R$, simply a change of symbols to make clear the non-dimensionalisation of units.
    \item The figure has been updated with a power law of $k^{-3}$ 
    \item The time $t^*$ was introduced as the time at which we observe a sufficient decay of the helical force ratio, where the difference is around 5\% between the positive and negative modes and remains relatively stable afterwards. In order to make this clearer, we have added a sente nce in the text to explicity state this.
    \item The value of 0.1s comes from dimensionalising the values of $\tau=0.01$ for $T=1.9K$ and $\tau=0.005$ for $T=2.1K$, using the values of $\tilde{\tau}$ listed in the supplementary materials. 
    \item Incorrect reference corrected as noted by the reviewer.
\end{enumerate}
\end{document}

### 2025-06-13 main_REV.tex
Added revised latex file

	\end{subfigure} \hfill
    %
	\begin{subfigure}[b]{0.24\textwidth}
		\centering
		\includegraphics*[width=\textwidth]{snaps-hel-1.pdf}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\textwidth}
		\centering
		\includegraphics*[width=\textwidth]{snaps-hel-2.pdf}
	\end{subfigure}
    \begin{subfigure}[b]{0.24\textwidth}
		\centering
		\includegraphics*[width=\textwidth]{snaps-hel-3.pdf}
	\end{subfigure}
    \begin{subfigure}[b]{0.24\textwidth}
		\centering
		\includegraphics*[width=\textwidth]{snaps-hel-4.pdf}
	\end{subfigure} \hfill
	\caption{
Three-dimensional rendering of the time evolution of
an initially orthogonal vortex configuration 
undergoing a vortex reconnection at $T = 1.9$K at dimensionless
times (from left to right)
$(t-t_R)/\tau_R=-7.47\times10^{-2}$, $-3.09\times10^{-3}$, $8.79\times10^{-4}$ and $5.39\times10^{-3}$, where $\tau_R = E^{1/2}_R/ L_R$. The green
tubes represent the superfluid vortex lines (the tubes’ radii have been 
greatly exaggerated for visual purpose). In the top sequence,
the blue volume rendering represents the scaled normal fluid enstrophy 
$\bom^2/\bom^2_{max}$. Note the Kelvin wave on the superfluid
vortex at $(t-t_0)/\tau_R=8.79\times10^{-4}$ . In the bottom sequence, the red/blue volume
rendering at the same times represent scaled positive/negative normal fluid
helicity.	
%Three-dimensional rendering of an orthogonal vortex configuration 
%undergoing a vortex reconnection at $T=1.9K$. The red tubes represent
%the superfluid vortex
%lines (the tubes' radii have been greatly exaggerated for visual purposes), 
%and the blue volume rendering represents the scaled normal fluid enstrophy 
%$\bom^2/\bom^2_{max}$. In the third panel, note the Kelvin waves on the superfluid vortices.
}
    \label{fig:visualisation}
\end{figure*}

%\paragraph*{Introduction.---} 
Turbulence is ubiquitous in the universe.  It occurs in systems
as large as nebulae of interstellar gas, and as small as clouds of
few thousands atoms confined by lasers in the laboratory.
Turbulence shapes patterns and properties of fluids of all
kinds, from ordinary
 viscous fluids (Navier-Stokes turbulence\cite{frisch1995}) 
to electrically conducting fluids (magneto-hydrodynamics turbulence
\cite{canuto-dalsgaard-1998}) to quantum fluid
(quantum turbulence \cite{barenghi-etal-2023,
Barenghi_Skrbek_Sreenivasan_2023}).
All turbulent systems are characterised by 
the existence of a wide range 
of length scales across which inviscid conserved quantities 
are transferred without loss in the spirit of the cascade 
depicted by Richardson \cite{richardson1922weather}.

@@

Remarkably, the same cascade phenomenology is observed in turbulent flows 
of quantum fluids, {\textit{i.e.} fluids at very low temperatures whose physics is
dominated by quantum effects.
Examples of such fluids are superfluid helium 
and atomic Bose-Einstein Condensates (BECs). 
The dynamics of these systems can be successfully depicted in terms of 
a two-fluid model \cite{tisza-1938,landau-1949,skrbek-sreenivasan-2012} 
describing the quantum fluid as the mixture of two components, 
the superfluid component and the thermal (or normal) component, which 
interact by means of a mutual friction force 
\cite{jackson-etal-2009,hall-vinen-1956a,hall-vinen-1956b}. 
The superfluid component flows without viscosity and
vanishing entropy; its vorticity is
confined to effectively one-dimensional vortex filaments
of atomic core thickness (called quantum vortices or vortex lines), 
around which the circulation of the velocity is quantised.
In BECs the thermal component forms a ballistic gas,
whereas in superfluid $^4$He it can be described as
a classical viscous fluid.
Despite these significant differences with respect to ordinary fluids, 
the direct
%forward 
kinetic energy cascade has
indeed been observed in three-dimensional superfluid
turbulence 
\cite{maurer1998,salort2010turbulent,baggaley2012,sherwin-robson2015,Muller_KolmogorovKelvinWave_2020,Muller_IntermittencyVelocityCirculation_2021}.
Evidence of this 
%forward 
direct
cascade has been found also in
three-dimensional turbulent BECs \cite{middleton-spencer2022}. Similarly to 2D classical turbulence, 
an inverse energy cascade characterises turbulence in two-dimensional BECs, 
as shown in theoretical \cite{bradley2012energy,reeves2013,simula2014emergence,Muller_ExploringEquivalenceTwoDimensional_2024} and experimental \cite{johnstone2019evolution,gauthier2019giant} studies.

@@

In this work, we unveil a similar dynamics occurring in superfluid helium
($^4$He) as a result of vortex reconnections.  
Reconnections occur continuously in turbulence: they take place when
two vortex lines collide and recombine, exchanging heads and tails, 
altering the overall topology of the flow
\cite{koplik-levine-1993,bewley-etal-2008,rorai-etal-2016,serafini-etal-2017,galantucci-baggaley-parker-barenghi-2019,villoisUniversalNonuniversalAspects2017,villois2020irreversible}. 
We show that the mutual friction force arising from the  
vortex reconnection is chiral, injecting in the normal fluid prevalently 
helicity of a given sign. Thus, as a consequence of vortex reconnections,
we observe an increase of the chiral imbalance of the quantum fluid, producing a transfer of kinetic energy from small to large scales, similarly to the phenomenology observed in 3D helical-decimated classical flows. 
 Unlike classical fluids, such a chiral imbalance arises naturally as physical process in the normal fluid.% because of vortex reconnections. 
%This is contrast to classical fluid dynamics,  where the helical characteristics of the flows producing 
% an inverse energy transfer require a careful synthetic construction 
% \cite{biferaleInverseEnergyCascade2012a,biferale-etal-2013,sahoo-etal-2017,plunianInverseCascadeEnergy2020a}.

@@

To study the reconnection dynamics, we consider two pairs of initially orthogonal vortices (where the corresponding vortices of each pair have opposite circulation in order to preserve periodicity along the boundaries)
at two distinct temperatures, $T=1.9K$ and $T=2.1K$. The vortex pairs are separated by the distance $D_{\ell}$; each vortex within each pair is initially at distance $d_{\ell}$ to the other vortex, such that $d_{\ell}\ll D_{\ell}$ to ensures that the dynamics in the vicinity of the reconnection is dominated by local interactions, and that the far-field contribution from the other vortex pair is negligible.

The evolution of the vortex reconnection of a single pair is reported in Fig.~\ref{fig:visualisation}. 
The first row shows the reconnecting superfluid vortices (in green) accompanied by normal fluid structures generated by mutual friction, here displayed as enstrophy rendering $\bom(\x)^2=|\nabla\times \v_n|^2$. Such structures are the signature of the violent irreversible energy transfers in vortex reconnections 
\cite{stasiak2024quantum}. The second row shows the rendering of the local helicity $H(\x)=\v_n\cdot\bom$, where we observe a clear local helicity production, with an abrupt change of sign due to the rearrangement of the vortex topology. Remarkably, during reconnection there is a net 
sudden normal fluid helicity production, as shown in Fig.~\ref{fig:total-helicity}. We will come back to this finding later.
\begin{figure}[t]
    \centering
    \includegraphics*[width=0.48\textwidth]{helicity_total}
\caption{Temporal evolution of the normal fluid helicity $\mathcal{H} = \int_{\mathcal{V}}H(\x)dV$ computed over the entire volume $\mathcal{V}$. For superfluid helium, it is proper to make the helicity dimensionless in terms of $\kappa^2$. The quantities $E_R$ and $L_R$ are the energy $E$ and integral length scales $L_0$ of the normal fluid at reconnection time $t_R$.}
\label{fig:total-helicity}
\end{figure}

We now focus on the time evolution of the normal fluid energy spectrum $E(k)$, defined by 
\begin{equation}
    E = \frac{1}{(2\pi)^3}\int_{\mathcal{V}}\frac{1}{2}|\v_n|^2 dV = \int_0^{\infty}E(k)dk
\end{equation}
where $E$ is the total normal fluid energy and $k$ is the magnitude of the three-dimensional wavenumber. The energy at reconnection $E_R$ is given by $E(t_R)$, where $t_R$ is the time at reconnection. The energy spectrum $E(k)$ is displayed in Fig.~\ref{fig:kinetic-energy}.
\begin{figure}[h!]
    \centering
    \begin{subfigure}{0.49\textwidth}
        \centering
        \includegraphics*[width=\textwidth]{energy-spec.pdf}
        \caption{}\label{fig:kinetic-energy}
    \end{subfigure}
    \begin{subfigure}{0.49\textwidth}
        \centering
        \includegraphics*[width=\textwidth]{flux-spec.pdf}
        \caption{}\label{fig:energy-flux}
    \end{subfigure}
    \caption{\emph{(a):} Normal fluid kinetic energy spectrum $E(k)$ before 
reconnection (dashed lines), at reconnection (solid lines) 
and after reconnection (dotted lines) for $T=1.9K$ (red)
and $T=2.1K$ (blue).\emph{(b):} Spectral normal fluid kinetic energy flux, $\Pi (k)$. It is normalised using the integral scale and the normal fluid energy at reconnection.
\emph{Inset:} Post reconnection evolution of the integral length scale, $L_0$.
Times and temperatures are labelled as in Fig.~\ref{fig:kinetic-energy}.}
\end{figure}
%

@@

% the dynamics of the normal fluid flow using the 
% spectral energy budget equation: 
% %
% \begin{equation}
%     \frac{\partial E(k)}{\partial t} = T(k) - D(k) + I(k)
% \end{equation}
% where $T(k)$ is the spectral kinetic energy transfer function,
% %(\textit{i.e.} $T(k)dk$ is the energy transfered per unit time by modes with $k < |\mathbf{k}| < k +dk$, determined by non-linear effects), 
% $D(k)=2\nu_n k^2 E_k$ is the dissipation spectrum and
% %=\mathrm{Re}(\hat{\mathbf{F}}_{ns}(\k)\cdot\hat{\v}^*(\k))$ 
% $I(k)$ is the injection spectrum arising from the mutual friction 
% force $\mathbf{F}_{ns}$.  
We observe that $\Pi(k) < 0$ for all $k$ during and after reconnection;
we also observe that, near the time of reconnection,
the peak value of $|\Pi(k)|$ is in the range $15 < k < 25$.
%
The negative sign of $\Pi(k)$ is evidence of a flux of kinetic  energy from small to large scales, exciting larger and larger scales. % In other words, at non-zero temperatures,
% vortex reconnections trigger an inverse transfer of energy, 
% which implies the creation of large scale structures, visible
% in Fig.~\ref{fig:visualisation}} \NOTE{GK: the figure shows small scale structures...}
This behaviour is quantified by the evolution of the integral length scale $L_0$, defined as
\begin{equation}
    L_0 = \frac{\pi}{2 E}\int_0^{\infty}\frac{E(k)}{k}dk, %\Big/ \int_0^{\infty}\!\!E(k)dk.
\end{equation}
The inset of Fig.~\ref{fig:energy-flux} shows that
$L_0$ indeed  increases steadily in the post-reconnection regime. Note that times have been normalised by the largest eddy-turnover-time at the reconnection event, evidencing  it fast evolution.

@@

A chiral imbalance occurs if the mutual friction force is helical, 
\textit{i.e.} if the ratio $|f^+|^2/|f^-|^2 \neq 1$, with $|f^\pm|^2$ the total squared norm of the mutual friction components. 
In Fig.~\ref{fig:mutual-friction-decomp}, we show the temporal evolution of $|f^+|^2/|f^-|^2$, for both temperatures. 
%
\begin{figure}[h!]
    \centering
    \includegraphics*[width=0.48\textwidth]{fmfDecompFig.pdf}
    \caption{Temporal evolution of projected mutual friction force components $f^\pm$/ Inset: temporal evolution of total helical components.}.
    \label{fig:mutual-friction-decomp}
\end{figure}
%
It is apparent
that during and after the reconnection, the mutual friction force is strongly chiral,
injecting more negative helicity than positive helicity. 
As a result, the ratio $\mathcal{H}^+/\mathcal{H}^-$ 
(reported in the inset of Fig.~\ref{fig:mutual-friction-decomp}) 
decreases significantly at reconnection and remains smaller than unity even at later times, 
indicating that the flow is persistently chiral. We conclude that the reconnection triggers indeed a chiral imbalance.
From Fig.~\ref{fig:mutual-friction-decomp} we determine the non-dimensional timescale $\tau = (t^*-t_R)E_R^{1/2}/L_R$
during which the mutual friction force is chiral as a result of reconnections: $\tau \approx 0.01$ and $\tau \approx 0.005$
for $T=1.9$K and $T=2.1$K, respectively, corresponding dimensionally to $\tau \approx 0.1$s for both temperatures. 
In superfluid turbulence, the timescale between two consecutive reconnections can be smaller than $\tau$ provided that the
vortex line density $\mathcal{L}$ (length of vortices per unit volume) is larger than $10^8 \text{m}^{-2}$ \cite{stasiak2024quantum,barenghi2004},
a condition which is easily met in superfluid helium experiments \cite{roche2007,Babuin2014}.

@@

%\paragraph*{Closing remarks.---}
In conclusion, the reconnection of quantum vortices in the two-fluid regime
($T\gtrsim 1.5$K) not only injects punctuated
energy in the normal fluid \cite{stasiak2024quantum}, but also triggers in the normal fluid
a transfer of kinetic energy towards the large scales. 
%This inverse 
%energy transfer arises from the fact that the mutual friction force (injecting energy and 
%helicity in the normal fluid) is helical, as Kelvin waves develop on the vortices as a result of the reconnection itself.
%The helical character of the mutual friction produces a chiral imbalance in the normal fluid, driving this inverse transfer, as previously observed in turbulent Navier-Stokes flows
This inverse energy transfer arises from the helical character of the
friction generated by the Kelvin waves released by the reconnecting
cusp, which produces a chiral imbalance in the normal fluid, as 
previously observed in turbulent Navier-Stokes flows
\cite{biferaleInverseEnergyCascade2012a,plunianInverseCascadeEnergy2020a}.

Our findings have profound implications for the nature of turbulence in 
finite temperature superfluids. In circumstances where the vortex density 
$\mathcal{L}$ is large and where the isotropy of the vortex tangle 
is broken by external forcing, the chirality of the flow generated by the 
frequent reconnections may be strong enough to induce an inverse energy 
cascade \cite{notes_recon}.
%The asymmetry of the reconnecting vortex configurations is a key element; 
%when perfectly symmetrical vortex configurations (with corresponding 
%opposite vortex line orientations) reconnect, the injected helicity 
%globally cancels out, as verified in our study if we take also into 
%account the reconnection.
The microscopic mechanism that we have described is probably what
triggers the inverse energy cascade which is observed numerically in  
large-scale simulations of counterflow turbulence at large heat fluxes \cite{polanco2020}, which is
indeed inherently not isotropic.
%, hence triggering non-fully reconnections. 
Our work hence motivates further detailed studies of
the role played by helicity in superfluid dynamics 
\cite{dileoni2016,galantucci2021},
moving the emphasis from few vortex systems \cite{scheeler2014} 
to fully coupled superfluid turbulence.

@@

% \bibliography{references}% Produces the bibliography via BibTeX

@@

\begin{thebibliography}{55}%

@@

  {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume}

@@

  {journal} {Phys. Rev. X}\ }\textbf {\bibinfo {volume} {11}},\ \bibinfo

@@

  {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume}
  {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume}

@@

  {\bibinfo  {journal} {Phys. Rev. Fluids}\ }\textbf {\bibinfo {volume}

@@

@@

>>>>

	\end{subfigure} \hfill
    %
	\begin{subfigure}[b]{0.24\textwidth}
		\centering
		\includegraphics*[width=\textwidth]{snaps-hel-1.pdf}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\textwidth}
		\centering
		\includegraphics*[width=\textwidth]{snaps-hel-2.pdf}
	\end{subfigure}
    \begin{subfigure}[b]{0.24\textwidth}
		\centering
		\includegraphics*[width=\textwidth]{snaps-hel-3.pdf}
	\end{subfigure}
    \begin{subfigure}[b]{0.24\textwidth}
		\centering
		\includegraphics*[width=\textwidth]{snaps-hel-4.pdf}
	\end{subfigure} \hfill
	\caption{
Three-dimensional rendering of the time evolution of
an initially orthogonal vortex configuration 
undergoing a vortex reconnection at $T = 1.9$K at dimensionless
times (from left to right)
$(t-t_R)/\tau_R=-7.47\times10^{-2}$, $-3.09\times10^{-3}$, $8.79\times10^{-4}$ and $5.39\times10^{-3}$, where $\tau_R = L_R/E^{1/2}_R$. The quantities $E_R$ and $L_R$ are the energy $E$ and integral length scales \red{$L$} of the normal fluid at reconnection time $t_R$. The green
tubes represent the superfluid vortex lines (the tubes’ radii have been 
greatly exaggerated for visual purpose). In the top sequence,
the blue volume rendering represents the scaled normal fluid enstrophy 
$\bom^2/\bom^2_{max}$. Note the Kelvin wave on the superfluid
vortex at $(t-t_R)/\tau_R=8.79\times10^{-4}$ . In the bottom sequence, the red/blue volume
rendering at the same times represent scaled positive/negative normal fluid
helicity.	
%Three-dimensional rendering of an orthogonal vortex configuration 
%undergoing a vortex reconnection at $T=1.9K$. The red tubes represent
%the superfluid vortex
%lines (the tubes' radii have been greatly exaggerated for visual purposes), 
%and the blue volume rendering represents the scaled normal fluid enstrophy 
%$\bom^2/\bom^2_{max}$. In the third panel, note the Kelvin waves on the superfluid vortices.
}
    \label{fig:visualisation}
\end{figure*}

%\paragraph*{Introduction.---} 
Turbulence is ubiquitous in the universe.  It occurs in systems
as large as nebulae of interstellar gas, and as small as clouds of
few thousands atoms confined by lasers in the laboratory.
Turbulence shapes patterns and properties of fluids of all
kinds, from ordinary
 viscous fluids (Navier-Stokes turbulence\cite{frisch1995}) 
to electrically conducting fluids (magneto-hydrodynamics turbulence
\cite{canuto-dalsgaard-1998}) to quantum fluids
(quantum turbulence \cite{barenghi-etal-2023,
Barenghi_Skrbek_Sreenivasan_2023}).
All turbulent systems are characterised by 
the existence of a wide range 
of length scales across which inviscid conserved quantities 
are transferred without loss in the spirit of the cascade 
depicted by Richardson \cite{richardson1922weather}.

@@

Remarkably, the same cascade phenomenology is observed in turbulent flows 
of quantum fluids, {\textit{i.e.} fluids at very low temperatures whose physics is
dominated by quantum effects.
Examples of such fluids are superfluid helium 
and atomic Bose-Einstein Condensates (BECs). 
The dynamics of these systems can be successfully depicted in terms of 
a two-fluid model \cite{tisza-1938,landau-1949,skrbek-sreenivasan-2012} 
describing the quantum fluid as the mixture of two components, 
the superfluid component and the thermal (or normal) component, which 
interact by means of a mutual friction force 
\cite{jackson-etal-2009,hall-vinen-1956a,hall-vinen-1956b}. 
The superfluid component flows without viscosity and
vanishing entropy; its vorticity is
confined to effectively one-dimensional vortex filaments
of atomic core thickness (called quantum vortices or vortex lines), 
around which the circulation of the velocity is quantised.
In BECs the thermal component forms a ballistic gas,
whereas in superfluid $^4$He it can be described as
a classical viscous fluid.
Despite these significant differences with respect to ordinary fluids, 
the direct
%forward 
kinetic energy cascade has
indeed been observed in three-dimensional superfluid
turbulence 
\cite{maurer1998,salort2010turbulent,baggaley2012,sherwin-robson2015,Muller_KolmogorovKelvinWave_2020,Muller_IntermittencyVelocityCirculation_2021}.
Evidence of this 
%forward 
direct
cascade has been found also in
three-dimensional turbulent BECs \cite{middleton-spencer2022}. 
\red{
In this forward energy cascade a fundamental role is played by the dynamics and interactions of quantum vortices,
in particular by their reconnections, phenomena where  
two vortex lines collide and recombine, exchanging heads and tails, 
altering the overall topology of the flow
\cite{koplik-levine-1993,bewley-etal-2008,rorai-etal-2016,serafini-etal-2017,galantucci-baggaley-parker-barenghi-2019,villoisUniversalNonuniversalAspects2017,villois2020irreversible}.
Reconnections occur continuously in 3D quantum turbulence and are essential to
the energy transfer towards small scales by engendering the the breakdown of coherent vortex structures
and triggering the Kelvin-wave cascade \cite{vinen-2001}.
}
In 2D, similarly to classical turbulence, 
an inverse energy cascade characterises turbulence in two-dimensional BECs, 
as shown in theoretical \cite{bradley2012energy,reeves2013,simula2014emergence,Muller_ExploringEquivalenceTwoDimensional_2024} and experimental \cite{johnstone2019evolution,gauthier2019giant} studies.

@@

In this work, we unveil a similar dynamics occurring in superfluid helium
($^4$He) as a result of vortex reconnections. 
%\red{The onset and development of quantum turbulence is fundamentally driven by such reconnections, which facilitates energy transfer and the breakdown of coherent vortex structures.}  
%Reconnections occur continuously in turbulence: they take place when
%two vortex lines collide and recombine, exchanging heads and tails, 
%altering the overall topology of the flow
%\cite{koplik-levine-1993,bewley-etal-2008,rorai-etal-2016,serafini-etal-2017,galantucci-baggaley-parker-barenghi-2019,villoisUniversalNonuniversalAspects2017,villois2020irreversible}. 
We show that the mutual friction force arising from the  
vortex reconnection is chiral, injecting in the normal fluid prevalently 
helicity of a given sign 
%\red{which is not globally conserved across the reconnection event}. 
Thus, as a consequence of vortex reconnections,
we observe an increase of the chiral imbalance of the quantum fluid, producing a transfer of kinetic energy from small to large scales, similarly to the phenomenology observed in 3D helical-decimated classical flows. 
 Unlike classical fluids, such a chiral imbalance arises naturally as physical process in the normal fluid.% because of vortex reconnections. 
%This is contrast to classical fluid dynamics,  where the helical characteristics of the flows producing 
% an inverse energy transfer require a careful synthetic construction 
% \cite{biferaleInverseEnergyCascade2012a,biferale-etal-2013,sahoo-etal-2017,plunianInverseCascadeEnergy2020a}.

@@

To study the reconnection dynamics, we consider two pairs of initially orthogonal vortices (where the corresponding vortices of each pair have opposite circulation in order to preserve periodicity along the boundaries)
at two distinct temperatures, $T=1.9K$ and $T=2.1K$. The vortex pairs are separated by the distance $D_{\ell}$; each vortex within each pair is initially at distance $d_{\ell}$ to the other vortex, such that $d_{\ell}\ll D_{\ell}$ to ensures that the dynamics in the vicinity of the reconnection is dominated by local interactions, and that the far-field contribution from the other vortex pair is negligible. \red{In our simulations, we consider only the vortex dynamics up to and shortly after the first reconnection, as the reconnection events occur asynchronously (see Fig.~\ref{fig:total-helicity}). Hence, all results reported and discussed herafter refer to the first reconnection.}.

The evolution of the vortex reconnection of a single pair is reported in Fig.~\ref{fig:visualisation}. 
The first row shows the reconnecting superfluid vortices (in green) accompanied by normal fluid structures generated by mutual friction, here displayed as enstrophy rendering $\bom(\x)^2=|\nabla\times \v_n|^2$. Such structures are the signature of the violent irreversible energy transfers in vortex reconnections 
\cite{stasiak2024quantum}. The second row shows the rendering of the local helicity $H(\x)=\v_n\cdot\bom$, where we observe a clear local helicity production, with an abrupt change of sign due to the rearrangement of the vortex topology. Remarkably, during reconnection there is a net 
sudden normal fluid helicity production, as shown in Fig.~\ref{fig:total-helicity}. We will come back to this finding later.
\begin{figure}[t]
    \centering
    \includegraphics*[width=0.48\textwidth]{helicity_normal_fluid.pdf}
\caption{Temporal evolution of the normal fluid helicity $\mathcal{H} = \int_{\mathcal{V}}H(\x)dV$ computed over the entire volume $\mathcal{V}$. For superfluid helium, it is proper to make the helicity dimensionless in terms of $\kappa^2$. \red{The 3D rendering shows the asynchronous nature of the reconnections in the initial configuration, with the same colour scheme as in Fig.~\ref{fig:visualisation}.}}
\label{fig:total-helicity}
\end{figure}

We now focus on the time evolution of the normal fluid energy spectrum $E(k)$, defined by 
\begin{equation}
    E = \frac{1}{(2\pi)^3}\int_{\mathcal{V}}\frac{1}{2}|\v_n|^2 dV = \int_0^{\infty}E(k)dk
\end{equation}
where $E$ is the total normal fluid energy and $k$ is the magnitude of the three-dimensional wavenumber. The energy at reconnection $E_R$ is given by $E(t_R)$, where $t_R$ is the time at reconnection. The energy spectrum $E(k)$ is displayed in Fig.~\ref{fig:kinetic-energy}.
\begin{figure}[h!]
    \centering
    \begin{subfigure}{0.49\textwidth}
        \centering
        \includegraphics*[width=\textwidth]{energy-spec.pdf}
        \caption{}\label{fig:kinetic-energy}
    \end{subfigure}
    \begin{subfigure}{0.49\textwidth}
        \centering
        \includegraphics*[width=\textwidth]{flux-spec.pdf}
        \caption{}\label{fig:energy-flux}
    \end{subfigure}
    \caption{\emph{(a):} Normal fluid kinetic energy spectrum $E(k)$ before 
reconnection (dashed lines), at reconnection (solid lines) 
and after reconnection (dotted lines) for $T=1.9K$ (red)
and $T=2.1K$ (blue).\emph{(b):} Spectral normal fluid kinetic energy flux, $\Pi (k)$. It is normalised using the integral scale and the normal fluid energy at reconnection.
\emph{Inset:} Post reconnection evolution of the integral length scale, $L$.
Times and temperatures are labelled as in Fig.~\ref{fig:kinetic-energy}.}
\end{figure}
%

@@

% the dynamics of the normal fluid flow using the 
% spectral energy budget equation: 
% %
% \begin{equation}
%     \frac{\partial E(k)}{\partial t} = T(k) - D(k) + I(k)
% \end{equation}
% where $T(k)$ is the spectral kinetic energy transfer function,
% %(\textit{i.e.} $T(k)dk$ is the energy transfered per unit time by modes with $k < |\mathbf{k}| < k +dk$, determined by non-linear effects), 
% $D(k)=2\nu_n k^2 E_k$ is the dissipation spectrum and
% %=\mathrm{Re}(\hat{\mathbf{F}}_{ns}(\k)\cdot\hat{\v}^*(\k))$ 
% $I(k)$ is the injection spectrum arising from the mutual friction 
% force $\mathbf{F}_{ns}$.  
We observe that $\Pi(k) < 0$ for all $k$ during and after reconnection;
we also observe that, near the time of reconnection,
the peak value of $|\Pi(k)|$ is in the range $15 < k < 25$.
%
The negative sign of $\Pi(k)$ is evidence of a flux of kinetic  energy from small to large scales, exciting larger and larger scales. % In other words, at non-zero temperatures,
% vortex reconnections trigger an inverse transfer of energy, 
% which implies the creation of large scale structures, visible
% in Fig.~\ref{fig:visualisation}} \NOTE{GK: the figure shows small scale structures...}
This behaviour is quantified by the evolution of the integral length scale $L$, defined as
\begin{equation}
    L = \frac{\pi}{2 E}\int_0^{\infty}\frac{E(k)}{k}dk, %\Big/ \int_0^{\infty}\!\!E(k)dk.
\end{equation}
The inset of Fig.~\ref{fig:energy-flux} shows that
$L$ indeed  increases steadily in the post-reconnection regime. Note that times have been normalised by the largest eddy-turnover-time at the reconnection event, evidencing  it fast evolution.

@@

A chiral imbalance occurs if the mutual friction force is helical, 
\textit{i.e.} if the ratio $|f^+|^2/|f^-|^2 \neq 1$, with $|f^\pm|^2$ the total squared norm of the mutual friction components. 
In Fig.~\ref{fig:mutual-friction-decomp}, we show the temporal evolution of $|f^+|^2/|f^-|^2$, for both temperatures. 
%
\begin{figure}[h!]
    \centering
    \includegraphics*[width=0.48\textwidth]{fmfDecompFig.pdf}
    \caption{Temporal evolution of projected mutual friction force components $f^\pm$/ Inset: temporal evolution of total helical components.}.
    \label{fig:mutual-friction-decomp}
\end{figure}
%
It is apparent
that during and after the reconnection, the mutual friction force is strongly chiral,
injecting more negative helicity than positive helicity. 
As a result, the ratio $\mathcal{H}^+/\mathcal{H}^-$ 
(reported in the inset of Fig.~\ref{fig:mutual-friction-decomp}) 
decreases significantly at reconnection and remains smaller than unity even at later times, 
indicating that the flow is persistently chiral. We conclude that the reconnection triggers indeed a chiral imbalance.
\red{
For the sake of completeness, it is worth noting that the total helicity of the flow (obtained by adding the superfluid helicity to that of the normal fluid $\mathcal{H}$) is not conserved.
}
From Fig.~\ref{fig:mutual-friction-decomp}, \red{ we consider a time $t^*$ after reconnection where the ratio $|f^+|^2/|f^-|^2$ has sufficiently decayed to a roughly 5\% difference and} we determine the non-dimensional timescale \red{$\tau = (t^*-t_R)/\tau_R$} during which the mutual friction force is chiral as a result of reconnections: $\tau \approx 0.01$ and $\tau \approx 0.005$
for $T=1.9$K and $T=2.1$K, respectively, corresponding dimensionally to $\tau \approx 0.1$s for both temperatures. 
In superfluid turbulence, the timescale between two consecutive reconnections can be smaller than $\tau$ provided that the
vortex line density $\mathcal{L}$ (length of vortices per unit volume) is larger than $10^8 \text{m}^{-2}$ \cite{stasiak2024quantum,barenghi2004},
a condition which is easily met in superfluid helium experiments \cite{roche2007,Babuin2014}.

@@

%\paragraph*{Closing remarks.---}
In conclusion, the reconnection of quantum vortices in the two-fluid regime
($T\gtrsim 1.5$K) not only injects punctuated
energy in the normal fluid \cite{stasiak2024quantum}, but also triggers in the normal fluid
a transfer of kinetic energy towards the large scales. 
%This inverse 
%energy transfer arises from the fact that the mutual friction force (injecting energy and 
%helicity in the normal fluid) is helical, as Kelvin waves develop on the vortices as a result of the reconnection itself.
%The helical character of the mutual friction produces a chiral imbalance in the normal fluid, driving this inverse transfer, as previously observed in turbulent Navier-Stokes flows
This inverse energy transfer \red{is triggered by} the helical character of the
mutual friction, \red{directly arising from the} Kelvin waves released by the reconnecting
cusp, which produces a chiral imbalance in the normal fluid, as 
previously observed in turbulent Navier-Stokes flows
\cite{biferaleInverseEnergyCascade2012a,plunianInverseCascadeEnergy2020a}.

Our findings have profound implications for the nature of turbulence in 
finite temperature superfluids, \red{where vortex reconnections play a key role}. 
In circumstances where the vortex density 
$\mathcal{L}$ is large and where the isotropy of the vortex tangle 
is broken by external forcing (for instance thermal counterflows \cite{vinen-1957a}), 
the chirality of the flow generated by the 
frequent \red{non-symmetrical} reconnections may be strong enough to induce an inverse energy 
cascade \cite{notes_recon}.
%The asymmetry of the reconnecting vortex configurations is a key element; 
%when perfectly symmetrical vortex configurations (with corresponding 
%opposite vortex line orientations) reconnect, the injected helicity 
%globally cancels out, as verified in our study if we take also into 
%account the reconnection.
The microscopic mechanism that we have described \red{may be relevant in triggering}
the inverse energy cascade which is observed numerically in  
large-scale simulations of counterflow turbulence at large heat fluxes \cite{polanco2020}, which is
indeed inherently not isotropic.
%, hence triggering non-fully reconnections. 
Our work hence motivates further detailed studies of
the role played by helicity in superfluid dynamics 
\cite{dileoni2016,galantucci2021},
moving the emphasis from few vortex systems \cite{scheeler2014} 
to fully coupled superfluid turbulence.

@@

@@

\begin{thebibliography}{57}%

@@

  {\bibinfo  {journal} {Physical Review B}\ }\textbf {\bibinfo {volume}

@@

  {journal} {Physical Review X}\ }\textbf {\bibinfo {volume} {11}},\ \bibinfo

@@

@@

  {\bibinfo  {journal} {Physical Review Fluids}\ }\textbf {\bibinfo {volume}

@@

\bibitem [{\citenamefont {Vinen}(2001)}]{vinen-2001}%
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.~F.}\ \bibnamefont
  {Vinen}},\ }\bibfield  {title} {\bibinfo {title} {Decay of superfluid
  turbulence at a very low temperature: The radiation of sound from a kelvin
  wave on a quantized vortex},\ }\href
  {https://doi.org/10.1103/PhysRevB.64.134520} {\bibfield  {journal} {\bibinfo
  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {64}},\ \bibinfo
  {pages} {134520} (\bibinfo {year} {2001})}\BibitemShut {NoStop}%
  {\bibinfo  {journal} {Physical Review Letters}\ }\textbf {\bibinfo {volume}
  {\bibinfo  {journal} {Physical Review Letters}\ }\textbf {\bibinfo {volume}

@@

\bibitem [{\citenamefont {Vinen}(1957)}]{vinen-1957a}%
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.~F.}\ \bibnamefont
